Analysis of cloud enhancement events in a 30-year record of global solar irradiance at Thessaloniki, Greece

### 2024-09-11 article/article.Rmd
Commit 2024-09-11 11:08
Commit 2024-09-11 12:14

# Data availability {.unnumbered}

>>>>

# Reproducibility {.unnumbered}

The GHI data are available as hourly values in the WMO World Radiation Data Center[^1].The relevant source code is available in three repositories for
(a) the preparation of GHI data [@natsis_2024_13744467]
(b) the detection of clouds [@thanasis_n_2024_13744460] and
(c) the processes for this manuscript [@thanasis_n_2024_13744472].

[^1]: [http://wrdc.mgo.rssi.ru](http://wrdc.mgo.rssi.ru)
